Accounting for uncertainty in simulation greenhouse gas emissions from dairy cattle in Kenya

### 2022-06-01 Manuscript_analyses.Rmd
most figures ggized

```{r}
uncertainty::varscatter(in_var = GHG_simulation_scenarios$y$pc_milk_yield,
                        out_var = GHG_simulation_scenarios$y$pc_on_farm,
                        xlab = expression(Total~milk~yield~(kg~head^{-1}~year^{-1})),
                        ylab = expression(Total~emissions~(kg~CO[2]-eq~head^{-1}~year^{-1})))
```

*# NICE PLOT, but would be nicer still if this was also a ggplot figure. Kinda inconsistent if it isn't. Also can't save it with ggsave, so will need another way.*

@@

uncertainty::varscatter(in_var = dairy_households$y$pc_milk_yield,
                        out_var = dairy_households$y$CO2eq_per_milk,
                        xlab = expression(Total~milk~yield~(kg~head^{-1}~year^{-1})),
                        ylab = expression(Total~emissions~intensity~of~milk~production~(kg~CO[2]-eq~kg^{-1})))
```

@@

```{r varkernel}
uncertainty::varkernel(in_var = dairy_households$y$pc_milk_yield,
                        out_var = dairy_households$y$CO2eq_per_milk,
                        xlab = expression(Total~milk~yield~(kg~head^{-1}~year^{-1})),
                        ylab = expression(Total~emissions~intensity~of~milk~production~(kg~CO[2]-eq~kg^{-1})))
```

@@

graphics::plot(x = slice$slice$Output_values, 
                 y = slice$slice$Relative_probability, 
                 type = "l", 
                 ylab = "Relative probability", 
                 xlab = "Emissions intensity", 
                 col = "seagreen", 
                 lwd = 2)

ggplot(data=data.frame(CO2eq_per_milk=slice$resampled), aes(CO2eq_per_milk)) +
geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666") +
  ylab("Relative probability") +
    xlab(expression(Emission~density~of~milk~production~at~2000~kg~milk~per~capita~(XX~CO[2]-eq~kg^-1)))

ggsave("Fig_X_emission_density_all_farms.png")

@@

ggsave("Fig_X1_probability_of_intensity_reduction.png")

@@

@@

ggsave("Fig_XX_breed_reductions.png")

@@

ggplot(data = decreased_emissions_probability, aes(Base_yield, yield_increase)) + geom_contour_filled(aes(z=probability)) +
  stat_contour(breaks = c(0.9),aes(z=probability),col="black") +
  geom_point(data=impact_of_breed[which(impact_of_breed$milk_change>0),],aes(x=baseline,y=milk_change)) +
  ggtitle("Probability that emission intensity reductions occurred") + 
  xlab("Baseline milk yield per head and year (kg)") +
  ylab("Milk yield increase per head and year (kg)") 
ggsave("Fig_XX1_breed_probability_of_intensity_reduction.png")

>>>>

```{r, warning=FALSE, message=FALSE}
#uncertainty::varscatter(in_var = GHG_simulation_scenarios$y$pc_milk_yield,
#                        out_var = GHG_simulation_scenarios$y$pc_on_farm,
#                        xlab = expression(Total~milk~yield~(kg~head^{-1}~year^{-1})),
#                        ylab = expression(Total~emissions~(kg~CO[2]-eq~head^{-1}~year^{-1})))

plotdata<-data.frame(in_var=GHG_simulation_scenarios$y$pc_milk_yield,
                     out_var=GHG_simulation_scenarios$y$pc_on_farm,
                     Group="just one")

plot1 <- ggplot(plotdata, aes(x = in_var, y = out_var)) + 
  geom_point(shape = 20, color = "blue", size = 2) + 
  stat_smooth(method = "loessm", fullrange = TRUE) +
  geom_density_2d() +
  geom_rug(color="lightskyblue3") + 
  labs(y=expression(Total~emissions~(kg~CO[2]*'-eq'~head^{-1}~year^{-1})),
       x=expression(Total~milk~yield~(kg~head^{-1}~year^{-1}))) +
  theme_bw() +
  theme(legend.position = c(0.15, 0.9))

dens1 <- ggplot(plotdata, aes(x = in_var)) + 
  geom_histogram(aes(y = ..density..),
                 colour = 1, fill = "white") +
  geom_density(fill="lightskyblue3") + 
  geom_histogram(aes(y = ..density..),
                 colour = 1, alpha=0) + 
  theme_void() + 
  theme(legend.position = "none")

dens2 <- ggplot(plotdata, aes(x = out_var)) + 
  geom_histogram(aes(y = ..density..),
                 colour = 1, fill = "white") +
  geom_density(fill="lightskyblue3") + 
  geom_histogram(aes(y = ..density..),
                 colour = 1, alpha=0) + 
  theme_void() + 
  theme(legend.position = "none") + 
  coord_flip()

dens1 + plot_spacer() + plot1 + dens2 + 
  plot_layout(ncol = 2, nrow = 2, widths = c(4, 1), heights = c(1, 4))

ggsave("Fig_4_scatter_per_head_milk_emissions.png",width=5,height=3)

@@

```{r, warning=FALSE, message=FALSE}

#uncertainty::varscatter(in_var = dairy_households$y$pc_milk_yield,
#                        out_var = dairy_households$y$CO2eq_per_milk,
#                        xlab = expression(Total~milk~yield~(kg~head^{-1}~year^{-1})),
#                        ylab = expression(Total~emissions~intensity~of~milk~production~(kg~CO[2]-eq~kg^{-1})))

plotdata<-data.frame(in_var=dairy_households$y$pc_milk_yield,
                     out_var=dairy_households$y$CO2eq_per_milk,
                     Group="just one")

plot1 <- ggplot(plotdata, aes(x = in_var, y = out_var)) + 
  geom_point(shape = 20, color = "blue", size = 2) + 
  stat_smooth(method = "loess", fullrange = TRUE) +
  geom_density_2d() +
  geom_rug(color="lightskyblue3") + 
  labs(y=expression(Total~emissions~intensity~of~milk~production~(kg~CO[2]*'-eq'~kg^{-1})),
       x=expression(Total~milk~yield~(kg~head^{-1}~year^{-1}))) +
  theme_bw() +
  theme(legend.position = c(0.15, 0.9))

dens1 <- ggplot(plotdata, aes(x = in_var)) + 
  geom_histogram(aes(y = ..density..),
                 colour = 1, fill = "white") +
  geom_density(fill="lightskyblue3") + 
  geom_histogram(aes(y = ..density..),
                 colour = 1, alpha=0) + 
  theme_void() + 
  theme(legend.position = "none")

dens2 <- ggplot(plotdata, aes(x = out_var)) + 
  geom_histogram(aes(y = ..density..),
                 colour = 1, fill = "white") +
  geom_density(fill="lightskyblue3") + 
  geom_histogram(aes(y = ..density..),
                 colour = 1, alpha=0) + 
  theme_void() + 
  theme(legend.position = "none") + 
  coord_flip()

dens1 + plot_spacer() + plot1 + dens2 + 
  plot_layout(ncol = 2, nrow = 2, widths = c(4, 1), heights = c(1, 4))

ggsave("Fig_5_scatter_per_head_milk_emissions_intensity.png",width=7,height=7)

@@

```{r varkernel}
#uncertainty::varkernel(in_var = dairy_households$y$pc_milk_yield,
#                        out_var = dairy_households$y$CO2eq_per_milk,
#                        xlab = expression(Total~milk~yield~(kg~head^{-1}~year^{-1})),
#                        ylab = expression(Total~emissions~intensity~of~milk~production~(kg~CO[2]-eq~kg^{-1})))

ggplot(plotdata, aes(x = in_var, y = out_var)) +
  stat_density_2d(
    geom = "raster",
    aes(fill = after_stat(density)),
    contour = FALSE
    ) +
  scale_fill_viridis_c() + 
  labs(y=expression(Total~emissions~intensity~of~milk~production~(kg~CO[2]*'-eq'~kg^{-1})),
       x=expression(Total~milk~yield~(kg~head^{-1}~year^{-1}))) +
  theme_bw()

ggsave("Fig_6_surface_per_head_milk_emissions_intensity.png",width=7,height=7)

@@

#graphics::plot(x = slice$slice$Output_values, 
#                 y = slice$slice$Relative_probability, 
#                 type = "l", 
#                 ylab = "Relative probability", 
#                 xlab = "Emissions intensity", 
#                 col = "seagreen", 
#                 lwd = 2)

ggplot(data=data.frame(CO2eq_per_milk=slice$resampled), aes(CO2eq_per_milk)) +
geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666") +
  ylab("Relative probability") +
    xlab(expression(Emission~intensity~of~milk~production~at~2000~kg~milk~per~capita~(kg~CO[2]*'-eq'~kg^-1)))

ggsave("Fig_7_emission_density_all_farms.png")

@@

ggsave("Fig_8_probability_of_intensity_reduction.png", width=7,height=5)

@@

ggsave("Fig_9_breeds.png", width=7,height=5)

@@

ggsave("Fig_10_breed_reductions.png", width=7,height=5)

@@

ggplot(data = decreased_emissions_probability, aes(Base_yield, yield_increase)) + geom_contour_filled(aes(z=probability)) +
  stat_contour(breaks = c(0.9),aes(z=probability),col="black") +
  geom_point(data=impact_of_breed[which(impact_of_breed$milk_change>0),],aes(x=baseline,y=milk_change)) +
  ggtitle("Probability that emission intensity reductions occurred") + 
  xlab("Baseline milk yield per head and year (kg)") +
  ylab("Milk yield increase per head and year (kg)") 
ggsave("Fig_11_breed_probability_of_intensity_reduction.png", width=7,height=5)
